--- 
title: "Using Classroom Shared Drawing"
author: "Henrik Skov Midtiby"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Tutorial for Classroom Shared Drawing

Follow these steps:

1. Log on to the Classroom Shared Drawing system with your credentials on this site: <https://tekvideo.sdu.dk/draw>
1. Open the *teacher view*
1. Click on *Prepare teaching* - *Choose File* (TODO: find a coordinate system to use for this)
    - Crop image
1. Click on *Actions* - *Push private canvas to students*
1. Click on *Navigation* - *Open page to share with students*
    - You should now be able to see the student view, displaying the image that you uploaded earlier.
1. Draw something on the student canvas
1. Observe that the drawing also appears on the teacher view.


# 

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
